Laws for Creating Trust in the Blockchain Age

### 2017-08-23 tex/article.tex

Obtaining agreement from numerous parties during several of the stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}

>>>>

Obtaining agreement from numerous parties during several of the stages of property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, 
offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}
% RV: make a case why things like transparency are important:
The importance of transparency that blockchains offer is even more apparent 
when one considers regions in which public's trust has been damaged,
e.g., in war-torn Colombia,
and land registration requires the involvement of its citizens 
% RV: please add this to the bibliography and turn it into a footcite:
(\url{https://www.kadaster.nl/-/landrechten-voor-vrede-in-colombia}).
